A Bayesian statistical model is able to predict target-by-target selection behaviour in a human foraging task

### 2022-11-08 Revisions 2/manuscriptRevisions2.tex
proofs

For trials in which the model does a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in terms of proximity in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants. We can see this more clearly in Figure \ref{fig:qjep_path_lengths}: while our model does a good job of capturing the average total path length, there is considerable variation with some participants generating shorter paths and some longer. We can see  that this appears to be systematically related to how well our model can predict behaviour. Interestingly, these poorly predicted example trials appear to have very strong pS biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well. This fits with conjunction trials being harder for the model to predict, as these trials generally have fewer switches.

>>>>

For trials in which the model does a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in terms of proximity in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants. We can see this more clearly in Figure \ref{fig:qjep_path_lengths}: while our model does a good job of capturing the average total path length, there is considerable variation with some participants generating shorter paths and some longer. We can see  that this appears to be systematically related to how well our model can predict behaviour. Interestingly, in some cases, poorly predicted trials appear to have very strong pS biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well. This fits with conjunction trials being harder for the model to predict, as these trials generally have fewer switches.
